### 2023-03-17 manuscript.tex
final touch [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/d3c54909ec4078326089a0e58e4543abde78ce90.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/d3c54909ec4078326089a0e58e4543abde78ce90/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4444509768

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/333f7ee6d46deecccb5e62dd8edadd9210478b2e/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/333f7ee6d46deecccb5e62dd8edadd9210478b2e}{MMV-Lab/im2im-paper@333f7ee}
on March 16, 2023.

@@

Second, we compared different network backbone architectures, including the original fnet model {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, an enhanced UNet {[}\protect\hyperlink{ref-M7480NLD}{25}{]}, the attention UNet {[}\protect\hyperlink{ref-OCow1hly}{26}{]}, two transformer-based models, SwinUNETR {[}\protect\hyperlink{ref-ZWL3IrVc}{27}{]} and UNETR{[}\protect\hyperlink{ref-XCKUntOB}{28}{]} (all with center normalization). Inspecting the predictions on a holdout validation set suggested that fnet achieved the best performance, and the recent transformer-based models did not work well with in labelfree problems (ref. the second row and the ``c + fnet'' from the first row in Figure \ref{fig:labelfree}-B).

@@

The \emph{EmbedSeg}-type models were re-implemented according to the original paper {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]} following the generic boilerplate in \emph{MMV\_Im2Im}, with significant improvment. First of all, following the modular design of \emph{MMV\_Im2Im}, it is flexible to use different neural network models as the backbone. For 3D anisotropic microscopy image, the original backbone ERFNet {[}\protect\hyperlink{ref-XAkgs3Nh}{38}{]} doesn't take the anisotropic dimensions into account and therefore may not perform well or even not applicable. In this scenario, it is straighforward to employ another anisotropic neural network bone, such as the anisotropic U-Net in {[}\protect\hyperlink{ref-jM3v1UjQ}{19}{]} or the anisotropic version of Dynamic U-Net in MONAI. Second, we significantly improve training strategy. The original version requires pre-cropping patches centered around each instance and pre-calculated the center images and class images. This may generate a massive amount of additional data on the disk. More importantly, such pre-cropping makes data augmentation nearly impossible, except the simple ones like flipping (otherwise, the pre-calculated centers might be wrong), and also greatly undersamples around negative cases (e.g., background). For example, we have observed that for an Embedseg model training only with patches centered around instances, the model may suffer from degraded performance during inference when there are a large amound of background areas without any instances. Again, following the modular design of \emph{MMV\_Im2Im}, it is now possible to do on-the-fly data augmentation and patch sampling, even weighted patch sampling. Third, our improved \emph{Embedseg}-type models can accept an exclusion mask so that certain parts of the images can be ignored during training. This is especially useful for partially annotated ground truth. For large images, it could be extremely time-consuming to require every single instance to be annotated. The exclusion masks can effectively avoid this bottleneck. Another extension comparing to the original implementation was that the \emph{MMV\_Im2Im} package made sliding windowing inference straightforward, and therefore permitted easy handling of images of any size during inference in practice.

@@

\begin{figure}
\hypertarget{fig:instance}{%
\centering
\includegraphics[width=0.85\textwidth,height=\textheight]{images/embedseg.png}
\caption{(A) Results 2D instance segmentation of C. elegans. Some minor errors can be observed in the zoom-in window, which could be refined with post-processing. (B) Results of 3D nuclear instance segmentation from fluorescent images and brightfield images. The green box in the fluorescent image highlights a mitotic example. The side view panel shows the segmentation of one specific nucleus along the line annotated in the fluorescent image from the side.}\label{fig:instance}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:unsupervised}{%
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{images/unsupervised.png}
\caption{(A) Illustration of the unsupervised learning scheme and results in the 2D tight-junction segmentation problem. The yellow arrows indicate a region where the unsupervised learning method actually predicted better than the original segmentation results by classic image processing methods. (B) Example 3D segmentation results (only showing a middle z-slice) from models obtained by unsupervised learning.}\label{fig:unsupervised}
}
\end{figure}

@@

In general, there are mainly four major DL frameworks that could be applied to microscopy image-to-image transformation: supervised learning with a fully convolutional networks (FCN) type models, supervised learning with pix2pix type models, unsupervised learning to learn mapping between visual domains, and Self2Self-type self-supervised learning {[}\protect\hyperlink{ref-srrRoFXR}{43}{]}. The major difference between FCN based supervised learning and pix2pix based supervised learning is that the pix2pix framework extends an FCN model with an adversarial head as a discriminator to further improves the realism of the prediction. The major difference between the unsupervised framework and the self-supervised framework is that the unsupervised methods still requires examples of the target images, even though the source images and target images do not need to be from the same sample or pixel-wise aligned. But, the self-supervised framework would only need the original images, which could be really helpful when it is impossible to acquire the target images (e.g., there is no truely noise-free or artifact-free image).

@@

\leavevmode\vadjust pre{\hypertarget{ref-srrRoFXR}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{\textbf{DeStripe: A Self2Self Spatio-Spectral Graph Neural Network with Unfolded Hessian for Stripe Artifact Removal in Light-sheet Microscopy}
\CSLBlock{Yu Liu, Kurt Weiss, Nassir Navab, Carsten Marr, Jan Huisken, Tingying Peng} \emph{arXiv} (2022) \url{https://doi.org/gqrnwr}
\CSLBlock{DOI: \href{https://doi.org/10.48550/arxiv.2206.13419}{10.48550/arxiv.2206.13419}}}

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/d3c54909ec4078326089a0e58e4543abde78ce90/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/d3c54909ec4078326089a0e58e4543abde78ce90}{MMV-Lab/im2im-paper@d3c5490}
on March 17, 2023.

@@

Second, we compared different network backbone architectures, including the original fnet model {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, an enhanced UNet {[}\protect\hyperlink{ref-M7480NLD}{25}{]}, the attention UNet {[}\protect\hyperlink{ref-OCow1hly}{26}{]}, two transformer-based models, SwinUNETR {[}\protect\hyperlink{ref-ZWL3IrVc}{27}{]} and UNETR{[}\protect\hyperlink{ref-XCKUntOB}{28}{]} (all with center normalization). Inspecting the predictions on a holdout validation set suggested that fnet achieved the best performance, and the transformer-based models did not work well in labelfree problems (ref. the second row and the ``c + fnet'' from the first row in Figure \ref{fig:labelfree}-B).

@@

The \emph{EmbedSeg}-type models were re-implemented according to the original paper {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]} following the generic boilerplate in \emph{MMV\_Im2Im}, with significant improvment. First of all, following the modular design of \emph{MMV\_Im2Im}, it is flexible to use different neural network models as the backbone. For 3D anisotropic microscopy image, the original backbone ERFNet {[}\protect\hyperlink{ref-XAkgs3Nh}{38}{]} doesn't take the anisotropic dimensions into account and therefore may not perform well or even not applicable. In this scenario, it is straighforward to employ another anisotropic neural network bone, such as the anisotropic U-Net in {[}\protect\hyperlink{ref-jM3v1UjQ}{19}{]} or the anisotropic version of Dynamic U-Net in MONAI. Second, we significantly improve training strategy. The original version requires pre-cropping patches centered around each instance and pre-calculated the center images and class images. This may generate a massive amount of additional data on the disk. More importantly, such pre-cropping makes data augmentation nearly impossible, except the simple ones like flipping (otherwise, the pre-calculated centers might be wrong), and also greatly undersamples around negative cases (e.g., background). For example, we have observed that for an Embedseg model training only with patches centered around instances, the model may suffer from degraded performance during inference when there are a large amound of background areas without any instances. Again, following the modular design of \emph{MMV\_Im2Im}, it is now possible to do on-the-fly data augmentation and patch sampling, even weighted patch sampling. Third, our improved \emph{Embedseg}-type models can accept an exclusion mask so that certain parts of the images can be ignored during training. This is especially useful for partially annotated ground truth. For large images, it could be extremely time-consuming to require every single instance to be annotated. The exclusion masks can address this bottleneck. Another extension comparing to the original implementation was that the \emph{MMV\_Im2Im} package made sliding windowing inference straightforward, and therefore permitted easy handling of images of any size during inference.

@@

\begin{figure}
\hypertarget{fig:instance}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/embedseg.png}
\caption{(A) Results 2D instance segmentation of C. elegans. Some minor errors can be observed in the zoom-in window, which could be refined with post-processing. (B) Results of 3D nuclear instance segmentation from fluorescent images and brightfield images. The green box in the fluorescent image highlights a mitotic example. The side view panel shows the segmentation of one specific nucleus along the line annotated in the fluorescent image from the side.}\label{fig:instance}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:unsupervised}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/unsupervised.png}
\caption{(A) Illustration of the unsupervised learning scheme and results in the 2D tight-junction segmentation problem. The yellow arrows indicate a region where the unsupervised learning method actually predicted better than the original segmentation results by classic image processing methods. (B) Example 3D segmentation results (only showing a middle z-slice) from models obtained by unsupervised learning.}\label{fig:unsupervised}
}
\end{figure}

@@

In general, there are mainly four major DL frameworks that could be applied to microscopy image-to-image transformation: supervised learning with a fully convolutional networks (FCN) type models, supervised learning with pix2pix type models, unsupervised learning to learn mapping between visual domains, and Self2Self-type self-supervised learning {[}\protect\hyperlink{ref-tuObtXMR}{43}{]}. The major difference between FCN based supervised learning and pix2pix based supervised learning is that the pix2pix framework extends an FCN model with an adversarial head as a discriminator to further improves the realism of the prediction. The major difference between the unsupervised framework and the self-supervised framework is that the unsupervised methods still requires examples of the target images, even though the source images and target images do not need to be from the same sample or pixel-wise aligned. But, the self-supervised framework would only need the original images, which could be really helpful when it is impossible to acquire the target images (e.g., there is no truely noise-free or artifact-free image).

@@

\leavevmode\vadjust pre{\hypertarget{ref-tuObtXMR}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{\textbf{DeStripe: A Self2Self Spatio-Spectral Graph Neural Network with~Unfolded Hessian for~Stripe Artifact Removal in~Light-Sheet Microscopy}
\CSLBlock{Yu Liu, Kurt Weiss, Nassir Navab, Carsten Marr, Jan Huisken, Tingying Peng} \emph{Lecture Notes in Computer Science} (2022) \url{https://doi.org/grxqnw}
\CSLBlock{DOI: \href{https://doi.org/10.1007/978-3-031-16440-8_10}{10.1007/978-3-031-16440-8\_10}}}
